\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
reword and better linebreaking

\section{\PYGEOMETRY{} design and layout}
\PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \pyinline{pyg4ometry.geant4} contains all classes for 
Geant4 detector construction, \pyinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files. There are sub-packages for importing and 
exporting other geometry formats  \pyinline{pyg4ometry.fluka}, \pyinline{pyg4ometry.stl} and \pyinline{pyg4ometery.freecad} and converting between file formats 
\verb|pyg4ometry.convert|.

>>>>

\section{\PYGEOMETRY{} design and layout}
\PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \verb|pyg4ometry.geant4| contains all classes for 
Geant4 detector construction and \verb|pyg4ometry.gdml| provides the functionality for reading and writing GDML files. There are sub-packages for importing and 
exporting other geometry formats: \verb|pyg4ometry.fluka|, \verb|pyg4ometry.stl| and \verb|pyg4ometery.freecad|.  Lastly, the sub-package \verb|pyg4ometry.convert| 
is used for conversions between formats.
